### 2018-05-14 submission/manuscript.Rmd
update figure legends

**Figure 1: Normalized Fecal Number of OTUs.** The x-axis represents the different sub-sampling depths used and the y-axis is the normalized within individual number of OTUs. The red line represents the overall mean Z-score normalized number of OTUs for each respective HiFi DNA polymerase. The dashed black line represents the overall Z-score normalized mean number of OTUs.

**Figure 2:  Mock Sample Variability in Number of OTUs based on HiFi DNA Polymerase.** A) Sub-sampled to 1000 reads. B) Sub-sampled to 5000 reads. C) Sub-sampled to 10000 reads. The dotted line represents the number of OTUs generated when the mock reference sequences are run through the pipeline.

**Figure 3: Community Differences by Five-Cycle Intervals and Sub-sampling Depth.** A) Fecal samples within person difference based on the next 5-cycle PCR interval. B) Mock samples within replicate difference based on the next 5-cycle PCR interval.

**Figure 4: HiFi DNA Polymerase Per Base Error Rate in Mock Samples.** A) Error rate before the merger of sequences with pre.cluster and the removal of chimeras with VSEARCH. B) Error rate before the removal of chimeras with VSEARCH. C) Full pipeline. The error bars represent the 75% interquartile range of the median.

**Figure 5: HiFi DNA Polymerase Chimera Prevalence in Mock Samples.** A) Chimera sequence percentage before the merger of sequences with pre.cluster and the removal of chimeras with VSEARCH. B) Chimera sequence percentage before the removal of chimeras with VSEARCH. C) Full pipeline. The error bars represent the 75% interquartile range of the median.

**Figure 6: The Correlation between Number of OTUs and Chimeras.** A) Correlation before the merger of sequences with pre.cluster and the removal of chimeras with VSEARCH. B) Correlation before the removal of chimeras with VSEARCH. C) Correlation with full pipeline.

>>>>

**Figure 1: Total Number of OTUs in Fecal Samples by Number of Cycles.** The x-axis represents the different number of cycles used and the y-axis is the number of OTUs. The legend represents the color code for the 5 different HiFi DNA polymerases used. The range in the number of OTUs detected in the different fecal samples increased as cycle number increased. This range was also larger for specific HiFi DNA polymerases.

**Figure 2:  Total Number of OTUs in Mock Samples by Number of Cycles.** The x-axis represents the different number of cycles used and the y-axis is the number of OTUs. The legend represents the color code for the 5 different HiFi DNA polymerases used. The dotted black line represents the number of OTUs detected when only the references sequences are clustered. The range in the number of OTUs detected in the Mock samples increased as cycle number increased. This range was also larger for specific HiFi DNA polymerases.

**Figure 3: Bray-Curtis Community Differences by Five-Cycle Intervals.** A) within person differences based on the next 5-cycle PCR interval in fecal samples. B) Within replicate difference based on the next 5-cycle PCR interval in Mock samples.

**Figure 4: HiFi DNA Polymerase Error Rate in Mock Samples.** The error bars represent the 75% interquartile range of the median error rate.

**Figure 5: HiFi DNA Polymerase Chimera Prevalence in Mock Samples.** A) Precentage of chimeric sequences without the removal of chimeras with VSEARCH. C) Percentage of chimeric sequences with the removal of chimeras with VSEARCH. C) The total percent of chimeric sequences removed with VSEARCH by cycle number. The error bars represent the 75% interquartile range of the median.

**Figure 6: The Correlation between Number of OTUs and Chimeras in Mock Samples.**

### 2018-05-14 submission/manuscript.tex
update figure legends

\textbf{Figure 1: Normalized Fecal Number of OTUs.} The x-axis
represents the different sub-sampling depths used and the y-axis is the
normalized within individual number of OTUs. The red line represents the
overall mean Z-score normalized number of OTUs for each respective HiFi
DNA polymerase. The dashed black line represents the overall Z-score
normalized mean number of OTUs.

\textbf{Figure 2: Mock Sample Variability in Number of OTUs based on
HiFi DNA Polymerase.} A) Sub-sampled to 1000 reads. B) Sub-sampled to
5000 reads. C) Sub-sampled to 10000 reads. The dotted line represents
the number of OTUs generated when the mock reference sequences are run
through the pipeline.

\textbf{Figure 3: Community Differences by Five-Cycle Intervals and
Sub-sampling Depth.} A) Fecal samples within person difference based on
the next 5-cycle PCR interval. B) Mock samples within replicate
difference based on the next 5-cycle PCR interval.

\textbf{Figure 4: HiFi DNA Polymerase Per Base Error Rate in Mock
Samples.} A) Error rate before the merger of sequences with pre.cluster
and the removal of chimeras with VSEARCH. B) Error rate before the
removal of chimeras with VSEARCH. C) Full pipeline. The error bars
represent the 75\% interquartile range of the median.

\textbf{Figure 5: HiFi DNA Polymerase Chimera Prevalence in Mock
Samples.} A) Chimera sequence percentage before the merger of sequences
with pre.cluster and the removal of chimeras with VSEARCH. B) Chimera
sequence percentage before the removal of chimeras with VSEARCH. C) Full
pipeline. The error bars represent the 75\% interquartile range of the
median.

\textbf{Figure 6: The Correlation between Number of OTUs and Chimeras.}
A) Correlation before the merger of sequences with pre.cluster and the
removal of chimeras with VSEARCH. B) Correlation before the removal of
chimeras with VSEARCH. C) Correlation with full pipeline.

>>>>

\textbf{Figure 1: Total Number of OTUs in Fecal Samples by Number of
Cycles.} The x-axis represents the different number of cycles used and
the y-axis is the number of OTUs. The legend represents the color code
for the 5 different HiFi DNA polymerases used. The range in the number
of OTUs detected in the different fecal samples increased as cycle
number increased. This range was also larger for specific HiFi DNA
polymerases.

\textbf{Figure 2: Total Number of OTUs in Mock Samples by Number of
Cycles.} The x-axis represents the different number of cycles used and
the y-axis is the number of OTUs. The legend represents the color code
for the 5 different HiFi DNA polymerases used. The dotted black line
represents the number of OTUs detected when only the references
sequences are clustered. The range in the number of OTUs detected in the
Mock samples increased as cycle number increased. This range was also
larger for specific HiFi DNA polymerases.

\textbf{Figure 3: Bray-Curtis Community Differences by Five-Cycle
Intervals.} A) within person differences based on the next 5-cycle PCR
interval in fecal samples. B) Within replicate difference based on the
next 5-cycle PCR interval in Mock samples.

\textbf{Figure 4: HiFi DNA Polymerase Error Rate in Mock Samples.} The
error bars represent the 75\% interquartile range of the median error
rate.

\textbf{Figure 5: HiFi DNA Polymerase Chimera Prevalence in Mock
Samples.} A) Precentage of chimeric sequences without the removal of
chimeras with VSEARCH. C) Percentage of chimeric sequences with the
removal of chimeras with VSEARCH. C) The total percent of chimeric
sequences removed with VSEARCH by cycle number. The error bars represent
the 75\% interquartile range of the median.

\textbf{Figure 6: The Correlation between Number of OTUs and Chimeras in
Mock Samples.}
